\gettitle

### 2019-11-02 assignment1/submission1.tex
Work on assignment 1.3

\section*{3 Three-Army-Problem}
\subsection*{a)}
\subsection*{b)}

>>>>

\section*{3 Three-Army-Problem}
\subsection*{a)}
To enable a resolution the failure model should exclude both crashing and byzantine failures.
General Omissions, so long as their occurences are bounded, can be resolved by retrying communication sufficiently often.
\subsection*{b)}
\par{Phase 1: Determining order of attack}
The initiating division sends a messenger with it's own size and the time \(t_0\) to both other divisions.
A division receiving a first message with a division size sends it's division size to the two other divisions.
If it has received two messages, it calculates the order of attack.
If it is the largest division it initiates Phase 2.
\par{Phase 2: Attack coordination}
The largest division is definitively known at \(t_1 = t_0 + r, r \leq 2d\).
The largest division attacks at \(t_1\) and sends a message with that time to both other divisions.
The second largest division attacks at time \(t_2 = t_1 + k\), the smallest division attacks at \(t_3 = t_1 + 2k = t_2 + k\).

Since all clocks are perfectly synchronized we only need to consider message delivery times.
\(t_1\) is minimal, because it's the first moment that the largest division is known to be the largest.
Since all divisions must have sent their size \emph{before} \(t_1\) -- otherwise the information would not be available -- all divisions know their position in the order of attack at \(t_1 + d < t_1 + k\), which implies that \(t_2 > t_1 + d\) as required to allow the second division to attack at the specified time.
And because all attacks must be at least \(k\) apart, \(2k\) is the minimal span of time between the first and last attack.

\begin{tikzpicture}
	% division identifiers
	\node[draw, circle] at (0, 5)   (D1) {\(D_1\)};
	\node[draw, circle] at (0, 2.5) (D2) {\(D_2\)};
	\node[draw, circle] at (0, 0)   (D3) {\(D_3\)};
	% division timelines
	\path[draw,->]
		(D1) -- (12, 5)
		(D2) -- (12, 2.5)
		(D3) -- (12, 0);
	% message 1 at t_0
	\node[draw, circle, fill=black] at (1, 5) (M1) {};
	\node[above=1.2, right=0.2]     at (1, 5) {\(t_0\)};
	% message 2 (coming from d3)
	\node[draw, circle, fill=black] at (2, 0) (M2) {};
	% message 3 (coming from d2)
	\node[draw, circle, fill=black] at (3, 2.5) (M3) {};
	\node[above=1]                  at (3, 2.5) {\(t_1\)};
	% attack message (assuming d1 is largest and last to know)
	\node[draw, circle, fill=red] at (5, 5) (MA) {};
	% attack timings
	\node[draw, circle, fill=red] at (7.5, 2.5) {};
	\node[draw, circle, fill=red] at (10,  0) {};
	% message delivery
	\path[draw, ->]
		(M1) edge node[above, sloped] {\(\leq d\)} (M3)
		(M1) edge node[above, sloped] {\(\leq d\)} (M2)
		(M2) edge node[below, sloped] {\(\leq d\)} (4.5, 2.5)
		(M2) edge node[below, sloped] {\(\leq d\)} (MA)
		(M3) edge node[above, sloped] {\(\leq d\)} (4, 5)
		(M3) edge node[above, sloped] {\(\leq d\)} (4, 0)
		(MA) edge node[above, sloped] {\(\leq d\)} (6.5, 0)
		(MA) edge node[above, sloped] {\(\leq d\)} (7, 2.5)
		;
	\path[draw, dashed]
		% t_1 possible area
		(4, 6) -- (4, -1)
		(5, 6) -- (5, -1)
		% t_2
		(7.5, 6) -- (7.5, -1)
		% t_3
		(10, 6) -- (10, -1)
		;
	\node at (4, 6) {\parbox{1.8cm}{Range of possible \(t_1\)}};
	\node at (5, -1.5) {\(t_1\)};
	\node at (7.5, -1.5) {\(t_2\)};
	\node at (10, -1.5) {\(t_3\)};

\end{tikzpicture}
